%!TEX TS-program = xelatex
\documentclass[]{friggeri-cv}
\addbibresource{bibliography.bib}

\begin{document}
\header{alexandre}{gerona}
       {full-stack. android.}


% In the aside, each new line forces a line break
\begin{aside}
  \section{about}
    Manila
    ~
    \href{https://alecgerona.io}{alecgerona.io}
    \href{mailto:alecgerona.com}{alecgerona@gmail.com}
    \href{github.com/alecgerona}{github.com/alecgerona}
    \href{https://gitlab.com/alecgerona}{gitlab.com/alecgerona}
  \section{stack}
    Python, Fastapi
    Flask, Django
    Vue, React
    Gatsby, Nuxt
    Angular
    Android
    RabbitMQ
    Docker
\end{aside}

\section{experience}

\begin{entrylist}
  \entry
    {10 2017 -}
    {\href{firstdigitalfinance.com}{First Digital Finance Corporation, Manila}}
    {Team Lead, Full-stack Developer}
    {\emph{Develop company projects from specification to delivery. I share responsibilities on the technical and often times creative direction of the company projects together with the CTO. I've led and developed multiple internal API microservices in Python in Docker containers with RabbitMQ for queues.
}}
  \entry
    {02–09 2017}
    {Vinteo Tech, Manila}
    {Consultant, Front-end Developer}
    {\emph{Consultant and developer for web app clients such as Unilab.}}
  \entry
    {02–09 2017}
    {\href{http://breakroad.com/}{BreakRoad35, Manila}}
    {Consultant, Front-end Developer}
    {\emph{Development of the admin dashboard for the backend office.}}
  \entry
    {04–05 2014}
    {\href{http://www.asiatype.com/}{Asiatype Inc., Manila}}
    {Development Internship}
    {\emph{Development of an internal project tracking system.}}
\end{entrylist}

\section{opensource}
\begin{entrylist}
  \entry
    {2020}
    {Pact Python}
    {\href{https://github.com/pact-foundation/pact-python}{github.com/pact-foundation/pact-python}}
    {Python version of Pact. Enables consumer driven contract testing, providing a mock service and DSL for the consumer project, and interaction playback and verification for the service provider project.}
  \entry
    {2020}
    {Commitizen Python}
    {\href{https://github.com/commitizen-tools/commitizen}{github.com/commitizen-tools/commitizen}}
    {Commitizen is a tool designed for teams to define a standard way of committing rules.}
  \entry
    {2020}
    {alecgerona.io}
    {\href{https://github.com/alecgerona/alecgerona.io}{github.com/alecgerona/alecgerona.io}}
    {My personal website and blog used to publish my tutorials or tech speak. Built with Gatsby/React.}
  \entry
    {2020}
    {pyrmq}
    {\href{https://github.com/first-digital-finance/pyrmq}{github.com/first-digital-finance/pyrmq}}
    {Python with RabbitMQ—simplified so you won't have to. PyRMQ is a python library available in PyPI built to simplify the bootstrapping needed for Python apps to integrate with RabbitMQ using Pika. It exposes several helper classes that handles settings and retries. It's currently in use and battle-tested in FDFC's python services.}
\end{entrylist}

\break
\break
\break

\section{applications}

\begin{entrylist}
  \entry
    {2019}
    {Billease.ph Mobile App}
    {\href{https://play.google.com/store/apps/details?id=ph.billeasev2.mobile}{BilleasePH @ Google Play Store}}
    {Android app counterpart of BillEase.ph. }
  \entry
    {2017}
    {Billease.ph and LoanRanger.ph}
    {\href{https://billease.ph}{billease.ph}}
    {Online financing service platforms. Built from the ground up that is fully integrated with
    internal company services. Built with Angular and Django, I was in charge of fleshing out the initial release with multiple features that integrates with internal company services, security improvements, additional API specs and implementation, automated testing, and devops.}
  \entry
    {2017}
    {Unilab Online Brand Reception Survey}
    {\href{https://www.unilab.com.ph/}{unilab.com}}
    {Online interactive survey that aims to gauge customers' recognition and retention of company brands.}
\end{entrylist}

\section{education}

\begin{entrylist}
  \entry
    {2012–2016}
    {BS Computer Science}
    {University of the Philippines Los Ba{\~{n}}os}
    {Project Schuyler: A Platform for Creating and Viewing Non-linear Interactive Videos for Teaching and Learning}
  \entry
    {2014–2015}
    {Foreign Exchange Student}
    {Far East University - South Korea}
    {Global Leadership Training Program, Business and International Relationship courses}
  \entry
    {2011-2012}
    {BS Mathematics and Science Teaching}
    {University of the Philippines Los Ba{\~{n}}os}
    {Specialization in mathematics}
\end{entrylist}
\end{document}
